Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-09 p2/ordering.tex
New acyclic ordering relation

We define $\ordersetsign$ with the help of a partial order.
\begin{mydef}[$\orderrel$]\mlabel{def_orderrel}
The binary relation $\orderrel$ holds for some command pairs
on directly related nodes if they are
of the following form:
\begin{itemize}
\item $\caaa{x}{\vald}{\parentf{n}}\orderrel\caaa{z}{w}{n}$, and
\item $\caaa{x}{\empt}{n}\orderrel\caaa{z}{w}{\parentf{n}}$.
\end{itemize}
\end{mydef}
This relation is clearly irreflexive and asymmetric,
and thus defines a partial order.

@@

The principal ideas behind the ordering are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if a simple sequence contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{simple_distant_pairs}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating these pairs we see that they are identified by the output value of the first command ($y$),
which in turn determines whether the command on the parent or the child must precede the other.

@@

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $\wrksx{S}$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
We use an inverse proof and assume $\wrksx{S'}$.
If $S'\not\in\orderset{S}$ then by \cref{def_orderrel,def_orderset}
it contains two commands on a node $n$ and its parent
that, as a subsequence,
do not form a construction or destruction pair.
However, this contradicts \cref{simple_distant_pairs}
which means that no such subsequence exists.
\end{proof}

@@

As a command cannot be both a construction and a destruction command,
this means that the indices $I^S$ are either monotone increasing, or monotone
decreasing, but cannot change direction.
And as $S$ begins with $\cxynv$ and so $I^S_0=1$, we know they are monotone increasing,
and the commands on $n_\indx$ are construction commands.
If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
by definition this means that
% $[y_\indx]\neq[\empt]$ for all $\indx$.
$y_\indx=\vald$ for all $\indx<k$.

Let us turn to the location of these commands in $T$,
and denote their indices in $T$ with $I^T_\indx$.
We know $I^T_k=I^T_0-1$ as $\czwmv$ precedes $\cxynv$.
This means there must exist a $1\leq \indx<k$ for which $I^T_{\indx+1}<I^T_\indx$.
We therefore know that
$\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{y_\indx}{n_\indx}$
is a subsequence of $T$.
Because we know $y_\indx=\vald$ and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
this has the form
$\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{\vald}{\parentf{n_{\indx+1}}}$.
If so, the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
% By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
% which is a contradiction.

It can be shown in the same way
that the case when the $n_\indx$ nodes ascend the tree,
that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction.
In this case we find that all commands are destruction commands,
and so 
% $[y_\indx]\neq[\vald]$, 
$y_\indx=\empt$ for all $1<\indx\leq k$,
which again leads to a subsequence in $T$ violating $\orderrel$.
% while in a subsequence of $T$ for a given $\indx$,
% $[y_\indx]=[\vald]$ must be true by definition of $\ordersetsign$.
\end{proof}

>>>>

We define $\ordersetsign$ with the help of a partial order.
\begin{mydef}[$\orderrel$]\mlabel{def_orderrel}
The binary relation $\orderrel$ holds for some command pairs
on directly related nodes in the following cases:
\begin{itemize}
\item $\caaa{x}{y}{\parentf{n}} \orderrel \caaa{z}{w}{n}$ if both commands are construction commands, and
\item $\caaa{x}{y}{n} \orderrel \caaa{z}{w}{\parentf{n}}$ if both commands are destruction commands.
\end{itemize}
\end{mydef}
This relation is clearly irreflexive and anti-symmetric,
and as a command cannot be both a construction and a destruction command and
the relation follows the tree of nodes, it is acyclic,
and thus defines a partial order.

@@

The principal ideas behind the ordering are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if a simple sequence contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{simple_distant_pairs}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
% Investigating these pairs we see that they are identified by the output value of the first command ($y$),
% which in turn determines whether the command on the parent or the child must precede the other.

@@

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $\wrksx{S}$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
We use an inverse proof and assume $\wrksx{S'}$.
If $S'\not\in\orderset{S}$ then by \cref{def_orderrel,def_orderset}
it contains two commands on a node $n$ and its parent
that, as a subsequence,
cannot form a construction or destruction pair.
However, this contradicts \cref{simple_distant_pairs}
which means that no such subsequence exists.
\end{proof}

@@

As a command cannot be both a construction and a destruction command,
this means that the indices $I^S$ are either monotone increasing, or monotone
decreasing, but cannot change direction.
And as $S$ begins with $\cxynv$ and so $I^S_0=1$, we know they are monotone increasing,
and the commands on $n_\indx$ are construction commands.
% If we denote the command on $n_\indx$ with $\caaa{x_\indx}{y_\indx}{n_\indx}$,
% by definition this means that
% $[y_\indx]\neq[\empt]$ for all $\indx$.
% -----
% $y_\indx=\vald$ for all $\indx<k$.

Let us turn to the location of these commands in $T$,
and denote their indices in $T$ with $I^T_\indx$.
We know $I^T_k=I^T_0-1$ as $\czwmv$ precedes $\cxynv$.
This means there must exist a $1\leq \indx<k$ for which $I^T_{\indx+1}<I^T_\indx$.
We therefore know that
$\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{y_\indx}{n_\indx}$
is a subsequence of $T$.
However, because we know these are construction commands, and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
% Because we know $y_\indx=\vald$ and by assumption $\parentf{n_{\indx+1}}=n_\indx$,
% this has the form
% $\caaa{x_{\indx+1}}{y_{\indx+1}}{n_{\indx+1}} \cc \caaa{x_\indx}{\vald}{\parentf{n_{\indx+1}}}$.
% If so, the inverse of $\orderrel$ holds for this subsequence, which is a contradiction.
% -----
% By definition of $\ordersetsign$, therefore $y_{\indx+1}=\empt$ must be true,
% which is a contradiction.

It can be shown in the same way
that the case when the $n_\indx$ nodes ascend the tree,
that is, $n_{\indx+1}=\parentf{n_\indx}$ is true, also leads to a contradiction.
In this case we find that all commands are destruction commands,
% and so 
% $[y_\indx]\neq[\vald]$, 
% $y_\indx=\empt$ for all $1<\indx\leq k$,
and a subsequence in $T$ again violates $\orderrel$.
% which again leads to a subsequence in $T$ violating $\orderrel$.
% while in a subsequence of $T$ for a given $\indx$,
% $[y_\indx]=[\vald]$ must be true by definition of $\ordersetsign$.
\end{proof}

### 2018-07-09 p2/upd-correct.tex
New acyclic ordering relation

\Cref{update_works} proves that $U$ functions as expected, that is, $U\aFS=\FS^*$.
While this is trivial if we know that $U$ does not break $\FS$, we
still need to show that it is defined.

On systems where filesystem updates a recorded,
an alternative update detection algorithm is to
omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates into a simple sequence containing the necessary
updates.
In fact, we use such a hypothetical record in the proof \cref{update_works}.

@@

An important consequence of this proof is that any sequence
of recorded updates that were applied to a filesystem can be
converted to a simple sequence using the rules listed in
\cref{section_axioms} alone.

>>>>

\Cref{update_works} proves that $U$ functions as expected, that is, $U\aFS=\FS^*$.
While this is trivial if we know that $U$ does not break $\FS$, we
still need to show that it is defined on $\FS$.

On systems where filesystem updates are recorded,
an alternative update detection algorithm is to
omit step 1, and use \cref{can_simplify} to simplify the series of recorded updates
into a simple sequence containing the necessary updates.
In fact, we use such a hypothetical record in the proof of \cref{update_works}.

@@
